% +--------------------------------------------------------------------+
% | Copyright Page
% +--------------------------------------------------------------------+

\newpage

\thispagestyle{empty}

\begin{center}

{\bf \Huge Abstract}

  \end{center}
\vspace{1cm}

The work presented focuses on the optimization of Artificial Intelligence (AI) algorithms, using MPI (Message Passing Interface), a standard library developed for high-performance computing.
The main objective consists of reducing the execution time of AI algorithms, exploiting the parallelism of computing resources and distributed memory. This task is especially relevant due to the high computational and resource cost involved in training or running these models.

This project includes a description of the theoretical foundations of the algorithms that will be implemented. Moreover, clarifying the functioning of the MPI library.
Once put in context, the strategies employed to enhance the algorithms are thoroughly elaborated upon.
And in addition, empirical study has been carried out to analyze the improvements developed throughout the project. This evaluation includes running the algorithms on a supercomputer with 128 cores.


\vspace{1cm}

% +--------------------------------------------------------------------+
% | On the line below, replace Fecha
% |
% +--------------------------------------------------------------------+

\begin{center}

{\bf \Large Keywords}

   \end{center}

   \vspace{0.5cm}
   
IA, machine learning, MPI, speedup, distributed memory, neural network, Evolutionary algorithm, clustering
   


